The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-09-03 razzo-discussion.tex
Depend on master branch

When simulating a DNA alignment, we chose to use the simplest (JC69) site
model and the simplest (strict) clock model. One could argue these models
are overly simplistic and biologically irrelevant. We argue that this
actually improves the clarity of our results for two reasons. The first
reason is a practical one: because the computational load was lowered,
we were able to perform more replicates. For a process with this
amount of stochaticity, we think this is highly favored. The second reason
is .. less noise,
more replicates.

 * Choice of generative (JC69 and strict) DNA alignment 
 * Choice of generative tree prior (BD)
 * Using Nested Sampling to do model comparison
 * Using the absolute nLTT statistic as an error function

>>>>

When simulating a DNA alignment, we chose to use the simplest (JC69) site
model and the simplest (strict) clock model. One could argue these models
are overly simplistic and biologically irrelevant. We argue that this
actually improves the clarity of our results for two reasons. The first
reason is a practical one: because the computational load was lowered,
we were able to perform more replicates. For a process with this high
amount of stochaticity, we think this is highly favored. The second reason
is that we think this reduces the noise of our results, without 
hurting the experiment: in our setup, it is essential
to assume the same generative site and clock model as the one that is actually 
used. Sure, we could have generated the alignment with a 
complex (GTR) site model and a complex (relaxed log-normal) clock model, then
correctly assume these were the generative site and clock model.
But that would be besides the point of the experiment: to measure the impact
of the tree prior.

For the generative tree prior, we picked the BD tree prior.

 * Choice of generative (JC69 and strict) DNA alignment

 * Choice of generative tree prior (BD)
 * Using Nested Sampling to do model comparison
 * Using the absolute nLTT statistic as an error function
